%-------------------------
% Resume in Latex
% Author : Mason Bane
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\educationDetail}[1]{%
  \vspace{-4pt}\item[]\small{#1}\vspace{-2pt}%
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Mason Bane} \\ \vspace{1pt}
    \small 817-487-5148 $|$ \href{mailto:mbane0525@gmail.com}{\underline{mbane0525@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/mason-bane/}{\underline{linkedin.com/in/mason-bane/}} $|$
    \href{https://github.com/MBane04}{\underline{github.com/MBane04}}
\end{center}


%-----------SUMMARY-----------
\vspace{-2pt}
\textbf{Summary:} Computer Science student (Computer Engineering) targeting embedded firmware and hardware/software integration roles. Proficient in microcontroller programming, low-level C/C++ and ARM Assembly, and circuit design. Strong mathematical/analytical skills with research experience.
\vspace{-4pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tarleton State University \textnormal}{Stephenville, TX}
      {Bachelor of Science in Computer Science, Concentration in Computer Engineering}
      {Aug. 2022 -- May 2026 (Expected)}
      \educationDetail{Minor in Mathematics}
      \educationDetail{GPA: 3.94/4.00 (Institutional) | Cumulative: 3.75/4.00}
   \resumeSubheading
      {Hill College}{Hillsboro, TX}
      {Associate of Arts in Liberal Arts}{Aug. 2019 -- Sept. 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Undergraduate Research Assistant}{May 2024 -- Present}
      {Tarleton State University}{Stephenville, TX}
      \resumeItemListStart
        \resumeItem{Contributed to the development and optimization of various N-Body simulations utilizing C/C++, enhancing computational efficiency and accuracy through advanced algorithms and parallel processing with CUDA.}
        \resumeItem{Collaborated with interdisciplinary teams to create digital twins to model complex problems using OpenGL and Blender, translating scientific concepts into interactive simulations and improving data interpretation.}
        \resumeItem{Conducted rigorous testing and debugging of simulation software, ensuring robust performance and reliability while documenting processes to facilitate knowledge transfer and future research initiatives.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Undergraduate Technology Specialist}{Aug. 2024 -- Present}
      {Tarleton State University}{Stephenville, TX}
      \resumeItemListStart
        \resumeItem{Managed and maintained 15 devices in a high-performance computer lab dedicated to research initiatives}
        \resumeItem{Performed system updates, hardware maintenance, and technical support, resolving issues promptly to minimize downtime and maintain optimal performance.}
        \resumeItem{Maintained a clean and organized lab environment, promoting a collaborative workspace that fosters innovation and productivity.}
    \resumeItemListEnd

%    \resumeSubheading
%      {Undergraduate Lab Instructor, Texas Government}{January 2023 -- December 2023}
%      {Tarleton State University}{Stephenville, TX}
%      \resumeItemListStart
%        \resumeItem{Guided and supported students in policy research and analysis, facilitating the exploration of bills and regulations to enhance critical thinking and analytical skills.}
%        \resumeItem{Conducted regular meetings and collaborated with the lecture professor and fellow lab leaders to align objectives and improve instructional methodologies, ensuring a cohesive educational experience.}
%      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{N-body Digital Twin of the Left Atrium } $|$ \emph{C/C++, CUDA, OpenGL, Blender, Bash}}{Aug. 2024 -- Present}
          \resumeItemListStart
				\resumeItem{Developed a CUDA-accelerated N-body model of the left atrium to simulate chaotic atrial arrhythmias, integrating anatomical data to explore potential treatments for atrial fibrillation.}
				\resumeItem{Built an interactive GUI using ImGui to streamline parameter adjustment and visualization, making the complex simulation accessible to a broader, non-technical audience.}
				\resumeItem{Presented findings at academic conferences, demonstrating the tool's potential to improve clinical decision-making and transform training for medical professionals.}
          \resumeItemListEnd
%      \resumeProjectHeading
%          {\textbf{N-Body Simulation of MicroPlastic-Polymer Interactions} $|$ \emph{C/C++, CUDA, OpenGL}}{May 2024 -- Aug. 2024}
%          \resumeItemListStart
%            \resumeItem{Contributed to the development and optimization a CUDA-based N-body simulation of Microplastic-Polymer interactions leveraging NVIDIA's CUDA technology for parallel processing and OpenGL for real-time 3D visualization, enhancing computational efficiency and user experience.}
%            \resumeItem{Crafted a user-friendly interface for toggling simulation features, providing enhanced visual cues and aiding in the understanding of complex phenomena.}
%            \resumeItem{Collaborated with a multidisciplinary team to define requirements, design features, and refine the simulation tool, ensuring alignment with project goals and user needs.}
%          \resumeItemListEnd
       \resumeProjectHeading
          {\textbf{Analog Pink Noise Generator Circuit} $|$ \emph{LTSpice, Python, MATLAB, Breadboarding}}{Aug. 2025 -- Dec. 2025}
          \resumeItemListStart
            \resumeItem{Designed and prototyped a BJT-based pink noise generator with active filter stage using LTSpice for simulation and breadboarding for physical implementation.}
            \resumeItem{Developed Python scripts to quantitatively compare simulation results with an ideal pink noise spectrum, guiding component selection and filter tuning for improved accuracy.}
            \resumeItem{Built a physical demonstration circuit with audio output, successfully verifying simulation models against real-world performance.}
             \resumeItem{Collaborated in a two-person team to present comprehensive design methodology, results, and data-driven decision process to peers and professors.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------Technical Skills-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: C/C++, Python, Java, ARM Assembly, Bash} \\
     \textbf{Embedded \& Hardware}{: TIVA-C Series (TM4C), Arduino, Raspberry Pi, GPIO} \\
     \textbf{Simulation \& Design Tools}{: LTSpice, MATLAB, Blender} \\
     \textbf{Systems \& Development}{: Git/GitHub, Linux, Visual Studio, VS Code, Make/CMake} \\
     \textbf{Parallel Computing \& Graphics}{: CUDA, OpenGL, ImGui} \\
             
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
